Comparing tool variability and numerical variability in fMRI analyses

### 2021-11-24 paper/paper.tex

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. All these software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 \discuss{to reproduce the results
in~\cite{bowring2019exploring} in a feasible execution time}. All the
analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
above-mentioned software packages in Docker container images available at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.

>>>>

We measured between-tool (BT) variability by running the pipelines
described in~\cite{bowring2019exploring} with FSL version 5.0.10, AFNI
version 18.1.09, and SPM12 version r7771 executed with GNU/Octave version
5.2. All these software versions were identical to the study
in~\cite{bowring2019exploring} except for SPM for which we used Octave
instead of MATLAB to enable mathematical function instrumentation using
Fuzzy Libmath. Indeed, MATLAB uses its own built-in mathematical functions,
which prevents the use of Fuzzy Libmath. In AFNI, we set the number of
threads to 7 even though AFNI executions
in~\cite{bowring2019exploring} were single-threaded. This was meant to
reduce the time overhead resulting from Fuzzy Libmath instrumentation. All
the analyses were conducted on the CentOS 7.3 operating system. The
computations were performed on \href{https://www.computecanada.ca}{Compute
Canada's} Béluga cluster nodes, each with 2$\times$ Intel Gold 6148 Skylake
@ 2.4 GHz (40 cores/node) CPU and 8~GB of RAM per core. We encapsulated the
above-mentioned software packages in Docker container images available at
\url{https://github.com/big-data-lab-team/fuzzy-neurotools}.
